---
title: "Exploratory Data Analysis"
author: "Stuart Miller"
date: "August 4, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup Environment

```{r, setup-env, message=FALSE}
# import libraries
library(knitr)
library(tidyverse)
library(naniar)
library(Hmisc)
library(GGally)
library(gridExtra)
library(RColorBrewer)
library(gplots)
library(corrplot)
library(ggthemes)

# import helper functions
source('../helper/data_munging.R')
source('../helper/visual.R')

# read in data
train <- read_csv('../data/CaseStudy2-data_train.csv')
```

# Data Exploration

A data dictionary was not given. So start by exploring the variables to get a sense of what is included. A simple data dictionary will be built. See './analysis/data/README.md' for more details.

```{r}
names(train)
```

# Reponse Variables

Two models are requested

* A model for salary, which is given as `MonthlyIncome` in the dataset.
* A model for attrition, which is given as `Attrition` in the dataset.

Histogram of monthly income reveals that it is highly skewed to the right.

```{r}
# histogram of MonthlyIncome
train %>% ggplot(aes(x = MonthlyIncome)) +
  geom_histogram(bins = 15)

# histogram of MonthlyIncome
train %>% ggplot(aes(x = log(MonthlyIncome))) +
  geom_histogram(bins = 15)
```

A bar plot of Attrition reveals that the response variable is highly imbalanced.

```{r}
# histogram of Attrition
train %>% ggplot(aes(x = Attrition)) +
  geom_bar()
```

# Explanatory - Continuous Variables

Exploration of the continuous variables.

```{r}
# create a vector of numeric features
features.numeric <- c('DailyRate', 'DistanceFromHome', 'Age', 'HourlyRate', 'MonthlyIncome', 'MonthlyRate',
           'NumCompaniesWorked','PercentSalaryHike', 'TotalWorkingYears', 'TrainingTimesLastYear',
           'YearsAtCompany','YearsInCurrentRole','YearsSinceLastPromotion', 'YearsWithCurrManager')
```


Explore features in isolation and the relationship between features and the response variables.

**Correlation to Response**

The following table ranks features in order of descending correlation to `MonthlyIncome`.

```{r, echo=T,warning=F, message=F}
train.numeric <- train %>% select(features.numeric)

correlation.matrix <- rcorr(as.matrix(train.numeric))
train.corToMI <- data.frame(flattenCorrMatrix(correlation.matrix$r, correlation.matrix$P)) %>% 
  filter(row == 'MonthlyIncome' | column == 'MonthlyIncome') %>%
  mutate(cor = abs(cor)) %>%
  arrange(-cor)
kable(train.corToMI)
```

**Correlation Heatmap**

`TotalworkingYears`, `Age`, `YearsAtCompany`, `YearsInCurrentRole`, and `YearsWithCurrentManager`.

```{r, fig.height = 10, fig.width = 10}
heatmap.cor <- function(df){
  df %>%
    keep(is.numeric) %>%
    drop_na() %>%
    cor %>%
    corrplot( addCoef.col = 'white',
             number.digits = 2,
             number.cex = 0.5,
             method = 'square')
}
heatmap.cor(train.numeric)
```


**Variance of Features**

The following table ranks features in order of descending standard deviation.

```{r}
# get varaince table
temp.table <- train %>%
  select(features.numeric) %>%
  summarise_all(funs(sd(.))) %>%
  rownames_to_column %>%
  gather(var, value, -rowname) %>%
  arrange(-value) %>%
  select(-one_of(c('rowname')))
# rename columns for clairity and print markdown table
names(temp.table) <- c('Feature','Standard Deviation')
kable(temp.table)
```

**Density Plots of All Numeric Features**

```{r, fig.height = 15, fig.width = 15}
train %>% keep(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(x = value)) + 
  facet_wrap(~ key, scales = 'free') + 
  geom_density() 
```



**`Age` exploration**

There appears to be a relationship between `Age` and `MonthlyIncome`. A relationship between `Age` and `Attrition` is not clear.

```{r}
train %>% ggplot(aes(x = Age)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = Age)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = Age, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`DailyRate` exploration**

There does not appear to be a correlation between `DailyRate` and either outcome variable.

```{r}
train %>% ggplot(aes(x = DailyRate)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = DailyRate)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = DailyRate, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`DistanceFromHome` exploration**

There does not appear to be a correlation between `DistanceFromHome` and either outcome variable.

```{r}
train %>% ggplot(aes(x = DistanceFromHome)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = DistanceFromHome)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = DistanceFromHome, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`MonthlyRate` exploration**

There does not appear to be a correlation between `MonthlyRate` and either outcome variable.

```{r}
train %>% ggplot(aes(x = MonthlyRate)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = MonthlyRate)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = MonthlyRate, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`PercentSalaryHike` exploration**

There does not appear to be a correlation between `PercentSalaryHike` and either outcome variable.

```{r}
train %>% ggplot(aes(x = PercentSalaryHike)) + 
  geom_histogram()

train %>% ggplot(aes(x = PercentSalaryHike)) + 
  geom_histogram() + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = PercentSalaryHike, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`TotalWorkingYears` exploration**

There does appear to be a correlation between `TotalWorkingYears` and `MonthlyIncome`.

```{r}
train %>% ggplot(aes(x = TotalWorkingYears)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = TotalWorkingYears)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = TotalWorkingYears, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`TrainingTimesLastYear` exploration**

There does not appear to be a correlation between `TrainingTimesLastYear` and either outcome variable.

```{r}
train %>% ggplot(aes(x = TrainingTimesLastYear)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = TrainingTimesLastYear)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = TrainingTimesLastYear, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`YearsAtCompany` exploration**

There does appear to be a correlation between `YearsAtCompany` and `MonthlyIncome`.

```{r}
train %>% ggplot(aes(x = YearsAtCompany)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = YearsAtCompany)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = YearsAtCompany, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`YearsInCurrentRole` exploration**

There does appear to be a correlation between `YearsInCurrentRole` and `MonthlyIncome`.

```{r}
train %>% ggplot(aes(x = YearsInCurrentRole)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = YearsInCurrentRole)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = YearsInCurrentRole, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`YearsSinceLastPromotion` exploration**

There does appear to be a correlation between `YearsSinceLastPromotion` and `MonthlyIncome`.

```{r}
train %>% ggplot(aes(x = YearsSinceLastPromotion)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = YearsSinceLastPromotion)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = YearsSinceLastPromotion, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`YearsWithCurrManager` exploration**

There does not appear to be a correlation between `YearsWithCurrManager` and either outcome variable.

```{r}
train %>% ggplot(aes(x = YearsWithCurrManager)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = YearsWithCurrManager)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = YearsWithCurrManager, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

## Multivariate Exploration

Scatter plot and correlation matrix gives a board overview of correlations between continuous variables.

* `MonthlyIncome` appears to be correlated with `Age` and `TotalWorkingYears`
* `YearsAtCompany`,`YearsInCurrentRole`,`YearsSinceLastPromotion`, `YearsWithCurrManager`, `TotalWorkingYears`, and `Age` appear to be correlated.

```{r, fig.height = 15, fig.width = 15, message=FALSE}
train %>%
  select(c(features.numeric)) %>%
  ggpairs()
```

**Look at log of MonthlyIncome `logMI` because MonthlyIncome is right skewed**

```{r, fig.height = 15, fig.width = 15, message=FALSE}
train <- train %>% mutate(logMI = log(MonthlyIncome))
train %>%
  select(c(features.numeric, 'logMI')) %>%
  ggpairs()
```

**Close up of MonthlyIncome and highest correlated features**

Taking the log of MonthlyIncome does not appear to improve linear correlation.

```{r, fig.height = 15, fig.width = 15, message=FALSE}
train %>%
  select(c('logMI','MonthlyIncome','Age','TotalWorkingYears','YearsAtCompany','YearsInCurrentRole',
           'YearsSinceLastPromotion','YearsWithCurrManager')) %>%
  ggpairs()
```

From the plot above, several of the variables appear to be linearly related: `YearsAtCompany` vs `YearsWithCurrManager`, `YearsInCurrentRole` and `YearsSinceLastPromotion`. This could be an interesting trend in the data.

```{r, message=FALSE}
p1 <- train %>% filter(YearsAtCompany > 0) %>%
  ggplot(aes(x = YearsWithCurrManager, y = YearsAtCompany)) + 
  geom_point() + geom_smooth(method = 'lm')
p2 <- train %>% filter(YearsAtCompany > 0) %>%
  ggplot(aes(x = YearsInCurrentRole, y = YearsAtCompany)) + 
  geom_point() + geom_smooth(method = 'lm')
p3 <- train %>% filter(YearsAtCompany > 0) %>%
  ggplot(aes(x = YearsSinceLastPromotion, y = YearsAtCompany)) + 
  geom_point() + geom_smooth(method = 'lm')
grid.arrange(p1,p2,p3, ncol = 2)
```

```{r}
m.YearsAtCompany <- train %>% 
  filter(YearsAtCompany > 0) %>% 
  lm(log(YearsAtCompany) ~ YearsSinceLastPromotion +  YearsInCurrentRole + YearsWithCurrManager, data = .)

summary(m.YearsAtCompany)

train %>% filter(YearsAtCompany > 0) %>%basic.fit.plots(., m.YearsAtCompany)
```

# Explanatory - factor Variables

Exploration of the continuous variables.

For investigation of the categrical variables, we will look at variables correlated to monthly income. Monthly income is correlated with `TotalworkingYears`, `Age`, `YearsAtCompany`, `YearsInCurrentRole`, and `YearsWithCurrentManager`.

```{r}
# create a vector of numeric features
features.factor <- c('BusinessTravel', 'Department', 'Education', 'EducationField', 'EmployeeNumber', 'EnvironmentSatisfaction', 'Gender', 'JobInvolvement', 'JobLevel', 'JobRole', 'JobSatisfaction', 'MaritalStatus', 'OverTime', 'PerformanceRating', 'RelationshipSatisfaction', 'StockOptionLevel', 'WorkLifeBalance')

# factor categorical variables
train[, features.factor] <- lapply(train[, features.factor], as.factor)
```

## BusinessTravel

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = BusinessTravel,
             y = log(MonthlyIncome),
             fill = BusinessTravel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = BusinessTravel,
             y = Age,
             fill = BusinessTravel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = BusinessTravel,
             y = YearsAtCompany,
             fill = BusinessTravel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = BusinessTravel,
             y = YearsWithCurrManager,
             fill = BusinessTravel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = BusinessTravel,
             y = TotalWorkingYears,
             fill = BusinessTravel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = Gender,
             y = log(MonthlyIncome),
             fill = Gender)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = Gender,
             y = Age,
             fill = Gender)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = Gender,
             y = YearsAtCompany,
             fill = Gender)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = Gender,
             y = YearsWithCurrManager,
             fill = Gender)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = Gender,
             y = TotalWorkingYears,
             fill = Gender)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = Department,
             y = log(MonthlyIncome),
             fill = Department)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = Department,
             y = Age,
             fill = Department)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = Department,
             y = YearsAtCompany,
             fill = Department)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = Department,
             y = YearsWithCurrManager,
             fill = Department)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = Department,
             y = TotalWorkingYears,
             fill = Department)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```



```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = Education,
             y = log(MonthlyIncome),
             fill = Education)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = Education,
             y = Age,
             fill = Education)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = Education,
             y = YearsAtCompany,
             fill = Education)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = Education,
             y = YearsWithCurrManager,
             fill = Education)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = Education,
             y = TotalWorkingYears,
             fill = Education)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = EducationField,
             y = log(MonthlyIncome),
             fill = EducationField)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = EducationField,
             y = Age,
             fill = EducationField)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = EducationField,
             y = YearsAtCompany,
             fill = EducationField)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = EducationField,
             y = YearsWithCurrManager,
             fill = EducationField)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = EducationField,
             y = TotalWorkingYears,
             fill = EducationField)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = EnvironmentSatisfaction,
             y = log(MonthlyIncome),
             fill = EnvironmentSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = EnvironmentSatisfaction,
             y = Age,
             fill = EnvironmentSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = EnvironmentSatisfaction,
             y = YearsAtCompany,
             fill = EnvironmentSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = EnvironmentSatisfaction,
             y = YearsWithCurrManager,
             fill = EnvironmentSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = EnvironmentSatisfaction,
             y = TotalWorkingYears,
             fill = EnvironmentSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = JobInvolvement,
             y = log(MonthlyIncome),
             fill = JobInvolvement)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = JobInvolvement,
             y = Age,
             fill = JobInvolvement)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = JobInvolvement,
             y = YearsAtCompany,
             fill = JobInvolvement)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = JobInvolvement,
             y = YearsWithCurrManager,
             fill = JobInvolvement)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = JobInvolvement,
             y = TotalWorkingYears,
             fill = JobInvolvement)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = JobLevel,
             y = log(MonthlyIncome),
             fill = JobLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = JobLevel,
             y = Age,
             fill = JobLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = JobLevel,
             y = YearsAtCompany,
             fill = JobLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = JobLevel,
             y = YearsWithCurrManager,
             fill = JobLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = JobLevel,
             y = TotalWorkingYears,
             fill = JobLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```


```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = JobRole,
             y = log(MonthlyIncome),
             fill = JobRole)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

btAg <- train %>% 
  ggplot(aes(x = JobRole,
             y = Age,
             fill = JobRole)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

btYAC <- train %>% 
  ggplot(aes(x = JobRole,
             y = YearsAtCompany,
             fill = JobRole)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

btYCM <- train %>% 
  ggplot(aes(x = JobRole,
             y = YearsWithCurrManager,
             fill = JobRole)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

btTWY <- train %>% 
  ggplot(aes(x = JobRole,
             y = TotalWorkingYears,
             fill = JobRole)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```



```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = JobSatisfaction,
             y = log(MonthlyIncome),
             fill = JobSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = JobSatisfaction,
             y = Age,
             fill = JobSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = JobSatisfaction,
             y = YearsAtCompany,
             fill = JobSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = JobSatisfaction,
             y = YearsWithCurrManager,
             fill = JobSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = JobSatisfaction,
             y = TotalWorkingYears,
             fill = JobSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```



```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = MaritalStatus,
             y = log(MonthlyIncome),
             fill = MaritalStatus)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = MaritalStatus,
             y = Age,
             fill = MaritalStatus)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = MaritalStatus,
             y = YearsAtCompany,
             fill = MaritalStatus)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = MaritalStatus,
             y = YearsWithCurrManager,
             fill = MaritalStatus)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = MaritalStatus,
             y = TotalWorkingYears,
             fill = MaritalStatus)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```



```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = OverTime,
             y = log(MonthlyIncome),
             fill = OverTime)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = OverTime,
             y = Age,
             fill = OverTime)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = OverTime,
             y = YearsAtCompany,
             fill = OverTime)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = OverTime,
             y = YearsWithCurrManager,
             fill = OverTime)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = OverTime,
             y = TotalWorkingYears,
             fill = OverTime)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```



```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = PerformanceRating,
             y = log(MonthlyIncome),
             fill = PerformanceRating)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = PerformanceRating,
             y = Age,
             fill = PerformanceRating)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = PerformanceRating,
             y = YearsAtCompany,
             fill = PerformanceRating)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = PerformanceRating,
             y = YearsWithCurrManager,
             fill = PerformanceRating)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = PerformanceRating,
             y = TotalWorkingYears,
             fill = PerformanceRating)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```



```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = RelationshipSatisfaction,
             y = log(MonthlyIncome),
             fill = RelationshipSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = RelationshipSatisfaction,
             y = Age,
             fill = RelationshipSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = RelationshipSatisfaction,
             y = YearsAtCompany,
             fill = RelationshipSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = RelationshipSatisfaction,
             y = YearsWithCurrManager,
             fill = RelationshipSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = RelationshipSatisfaction,
             y = TotalWorkingYears,
             fill = RelationshipSatisfaction)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = StockOptionLevel,
             y = log(MonthlyIncome),
             fill = StockOptionLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = StockOptionLevel,
             y = Age,
             fill = StockOptionLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = StockOptionLevel,
             y = YearsAtCompany,
             fill = StockOptionLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = StockOptionLevel,
             y = YearsWithCurrManager,
             fill = StockOptionLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = StockOptionLevel,
             y = TotalWorkingYears,
             fill = StockOptionLevel)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = WorkLifeBalance,
             y = log(MonthlyIncome),
             fill = WorkLifeBalance)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = WorkLifeBalance,
             y = Age,
             fill = WorkLifeBalance)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = WorkLifeBalance,
             y = YearsAtCompany,
             fill = WorkLifeBalance)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = WorkLifeBalance,
             y = YearsWithCurrManager,
             fill = WorkLifeBalance)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = WorkLifeBalance,
             y = TotalWorkingYears,
             fill = WorkLifeBalance)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

```{r, fig.width=15, fig.height=15}
btMI <- train %>% 
  ggplot(aes(x = Attrition,
             y = log(MonthlyIncome),
             fill = Attrition)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btAg <- train %>% 
  ggplot(aes(x = Attrition,
             y = Age,
             fill = Attrition)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYAC <- train %>% 
  ggplot(aes(x = Attrition,
             y = YearsAtCompany,
             fill = Attrition)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btYCM <- train %>% 
  ggplot(aes(x = Attrition,
             y = YearsWithCurrManager,
             fill = Attrition)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

btTWY <- train %>% 
  ggplot(aes(x = Attrition,
             y = TotalWorkingYears,
             fill = Attrition)) +
  geom_boxplot() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

grid.arrange(btMI, btAg, btYAC, btYCM, btTWY)
```

























