---
title: "Exploratory Data Analysis"
author: "Stuart Miller"
date: "August 4, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup Environment

```{r, setup-env, message=FALSE}
# import libraries
library(knitr)
library(tidyverse)
library(naniar)
library(Hmisc)
library(GGally)
library(gridExtra)

# import helper functions
source('../helper/data_munging.R')

# read in data
train <- read_csv('../data/CaseStudy2-data_train.csv')
```

# Data Exploration

A data dictionary was not given. So start by exploring the variables to get a sense of what is included. A simple data dictionary will be built. See './analysis/data/README.md' for more details.

```{r}
names(train)
```

# Reponse Variables

Two models are requested

* A model for salary, which is given as `MonthlyIncome` in the dataset.
* A model for attrition, which is given as `Attrition` in the dataset.

Histogram of monthly income reveals that it is highly skewed to the right.

```{r}
# histogram of MonthlyIncome
train %>% ggplot(aes(x = MonthlyIncome)) +
  geom_histogram(bins = 15)
```

A bar plot of Attrition reveals that the response variable is highly imbalanced.

```{r}
# histogram of Attrition
train %>% ggplot(aes(x = Attrition)) +
  geom_bar()
```

# Explanatory - Continuous Variables

Exploration of the continuous variables.

```{r}
# create a vector of numeric features
features.numeric <- c('DailyRate', 'DistanceFromHome', 'Age', 'HourlyRate', 'MonthlyIncome', 'MonthlyRate',
           'NumCompaniesWorked','PercentSalaryHike', 'TotalWorkingYears', 'TrainingTimesLastYear',
           'YearsAtCompany','YearsInCurrentRole','YearsSinceLastPromotion', 'YearsWithCurrManager')
```


## Univariate Analysis

Explore features in isolation and the relationship between features and the response variables.

**Correlation to Response**

The following table ranks features in order of descending correlation to `MonthlyIncome`.

```{r, echo=T,warning=F, message=F}
train.numeric <- train %>% select(features.numeric)

correlation.matrix <- rcorr(as.matrix(train.numeric))
train.corToMI <- data.frame(flattenCorrMatrix(correlation.matrix$r, correlation.matrix$P)) %>% 
  filter(row == 'MonthlyIncome' | column == 'MonthlyIncome') %>%
  mutate(cor = abs(cor)) %>%
  arrange(-cor)
kable(train.corToMI)
```

**Variance of Features**

The following table ranks features in order of descending standard deviation.

```{r}
# get varaince table
temp.table <- train %>%
  select(features.numeric) %>%
  summarise_all(funs(sd(.))) %>%
  rownames_to_column %>%
  gather(var, value, -rowname) %>%
  arrange(-value) %>%
  select(-one_of(c('rowname')))
# rename columns for clairity and print markdown table
names(temp.table) <- c('Feature','Standard Deviation')
kable(temp.table)
```


**`Age` exploration**

There appears to be a relationship between `Age` and `MonthlyIncome`. A relationship between `Age` and `Attrition` is not clear.

```{r}
train %>% ggplot(aes(x = Age)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = Age)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = Age, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`DailyRate` exploration**

There does not appear to be a correlation between `DailyRate` and either outcome variable.

```{r}
train %>% ggplot(aes(x = DailyRate)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = DailyRate)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = DailyRate, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`DistanceFromHome` exploration**

There does not appear to be a correlation between `DistanceFromHome` and either outcome variable.

```{r}
train %>% ggplot(aes(x = DistanceFromHome)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = DistanceFromHome)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = DistanceFromHome, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`MonthlyRate` exploration**

There does not appear to be a correlation between `MonthlyRate` and either outcome variable.

```{r}
train %>% ggplot(aes(x = MonthlyRate)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = MonthlyRate)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = MonthlyRate, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`PercentSalaryHike` exploration**

There does not appear to be a correlation between `PercentSalaryHike` and either outcome variable.

```{r}
train %>% ggplot(aes(x = PercentSalaryHike)) + 
  geom_histogram()

train %>% ggplot(aes(x = PercentSalaryHike)) + 
  geom_histogram() + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = PercentSalaryHike, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`TotalWorkingYears` exploration**

There does appear to be a correlation between `TotalWorkingYears` and `MonthlyIncome`.

```{r}
train %>% ggplot(aes(x = TotalWorkingYears)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = TotalWorkingYears)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = TotalWorkingYears, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`TrainingTimesLastYear` exploration**

There does not appear to be a correlation between `TrainingTimesLastYear` and either outcome variable.

```{r}
train %>% ggplot(aes(x = TrainingTimesLastYear)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = TrainingTimesLastYear)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = TrainingTimesLastYear, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`YearsAtCompany` exploration**

There does appear to be a correlation between `YearsAtCompany` and `MonthlyIncome`.

```{r}
train %>% ggplot(aes(x = YearsAtCompany)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = YearsAtCompany)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = YearsAtCompany, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`YearsInCurrentRole` exploration**

There does appear to be a correlation between `YearsInCurrentRole` and `MonthlyIncome`.

```{r}
train %>% ggplot(aes(x = YearsInCurrentRole)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = YearsInCurrentRole)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = YearsInCurrentRole, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`YearsSinceLastPromotion` exploration**

There does appear to be a correlation between `YearsSinceLastPromotion` and `MonthlyIncome`.

```{r}
train %>% ggplot(aes(x = YearsSinceLastPromotion)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = YearsSinceLastPromotion)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = YearsSinceLastPromotion, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

**`YearsWithCurrManager` exploration**

There does not appear to be a correlation between `YearsWithCurrManager` and either outcome variable.

```{r}
train %>% ggplot(aes(x = YearsWithCurrManager)) + 
  geom_histogram(bins = 15)

train %>% ggplot(aes(x = YearsWithCurrManager)) + 
  geom_histogram(bins = 15) + 
  facet_wrap(~ Attrition)

train %>% ggplot(aes(x = YearsWithCurrManager, y = MonthlyIncome)) + 
  geom_point() + geom_smooth(method = 'lm')
```

## Multivariate Exploration

Scatter plot and correlation matrix gives a board overview of correlations between continuous variables.

* `MonthlyIncome` appears to be correlated with `Age` and `TotalWorkingYears`
* `YearsAtCompany`,`YearsInCurrentRole`,`YearsSinceLastPromotion`, `YearsWithCurrManager`, `TotalWorkingYears`, and `Age` appear to be correlated.

```{r, fig.height = 15, fig.width = 15, message=FALSE}
train %>%
  select(c(features.numeric)) %>%
  ggpairs()
```

**Look at log of MonthlyIncome `logMI` because MonthlyIncome is right skewed**

```{r, fig.height = 15, fig.width = 15, message=FALSE}
train <- train %>% mutate(logMI = log(MonthlyIncome))
train %>%
  select(c(features.numeric, 'logMI')) %>%
  ggpairs()
```

**Close up of MonthlyIncome and highest correlated features**

Taking the log of MonthlyIncome does not appear to improve linear correlation.

```{r, fig.height = 15, fig.width = 15, message=FALSE}
train %>%
  select(c('logMI','MonthlyIncome','Age','TotalWorkingYears','YearsAtCompany','YearsInCurrentRole',
           'YearsSinceLastPromotion','YearsWithCurrManager')) %>%
  ggpairs()
```

From the plot above, several of the variables appear to be linearly related: `YearsAtCompany` vs `YearsWithCurrManager`, `YearsInCurrentRole` and `YearsSinceLastPromotion`. This could be an interesting trend in the data.

```{r, message=FALSE}
p1 <- train %>%
  ggplot(aes(x = YearsWithCurrManager, y = YearsAtCompany)) + 
  geom_point() + geom_smooth(method = 'lm')
p2 <- train %>%
  ggplot(aes(x = YearsInCurrentRole, y = YearsAtCompany)) + 
  geom_point() + geom_smooth(method = 'lm')
p3 <- train %>%
  ggplot(aes(x = YearsSinceLastPromotion, y = YearsAtCompany)) + 
  geom_point() + geom_smooth(method = 'lm')
grid.arrange(p1,p2,p3, ncol = 2)
```















