---
title: "Modeling Income"
author: "Stuart Miller"
date: "August 9, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}


# import libraries
library(knitr)
library(tidyverse)
library(naniar)
library(Hmisc)
library(GGally)
library(gridExtra)
library(RColorBrewer)
library(gplots)
library(corrplot)
library(ggthemes)
library(caret)

set.seed(3456)

# import helper functions
source('../helper/data_munging.R')
source('../helper/visual.R')

# read in data
train <- read_csv('../data/CaseStudy2-data_train.csv')
train$JobLevel <-  as.factor(train$JobLevel)
```

## Data Partitioning

The training dataset will be split into a training set and a test set. The training set `dfTrain` will be used for model cross validation. The test set will be used for final model selection.

```{r}
# split off a test set
trainIndex <- createDataPartition(train$MonthlyIncome , p = .75, 
                                  list = FALSE, 
                                  times = 1)
dfTrain <- train[trainIndex,]
dfTest <-  train[-trainIndex,]
```

## Helper Code

CV Runner - cross validate model on traning parition

```{r}
train.cv <- function(model, method, folds){
  # Set up repeated k-fold cross-validation
  train.control <-trainControl(method = "cv", number = folds)
  # Train the model
  model.cv <-dfTrain %>% train(model,
                   data = .,
                   method = method,
                   trControl = train.control)
  # print model summary
  model.cv
}
```

## Model Construction

From EDA, it appears that monthly income is correlated to `TotalworkingYears`, `Age`, `YearsAtCompany`, `YearsInCurrentRole`, and `YearsWithCurrentManager`.

From the factors:

* `JobLevel` appears to partion `TotalWorkingYears` and `MonthlyIncome` very well.
* `JobRole` appears to partion `MonthlyIncome` very well.

The following models will be used to for regression: `Linear Regression` and `k-Nearest Neighbors`.

### Linear Regression

Based on EDA, the following model will be used for linear regression:

$$ \mu \lbrace MonthlyIncome \rbrace = \beta_0 + \beta_1 (JobLevel) + \beta_2(JobRole) + \beta_3(JobLevel)(TotalWorkingYears) $$

Estimate model on whole dataset and create fit assessement plots.

```{r}
model.linear <- dfTrain %>% lm(MonthlyIncome ~ JobLevel + JobRole + TotalWorkingYears:JobLevel, data = .)

summary(model.linear)

dfTrain  %>% basic.fit.plots(., model.linear)
```

Cross-validate model with linear regression

```{r, cv_pipe}

model.formula <- MonthlyIncome ~ TotalWorkingYears:JobLevel + JobLevel + TotalWorkingYears:JobRole

# Eval model on 5 folds
lin.model.cv <- train.cv(model.formula, 'lm', 5)

# print model summary
lin.model.cv

# print md table with model performance
kable(data.frame('RMSE' = c(lin.model.cv$results$RMSE),
                 'Adj R Square' = c(lin.model.cv$results$Rsquared)))
```

### K Nearest Neighbors Regression

Since is a nonparametric model, a few correlated parameters will be added

```{r}
model.formula <- MonthlyIncome ~ TotalWorkingYears:JobLevel + JobLevel + JobLevel:Age + TotalWorkingYears:JobRole + JobRole

# Eval model on 5 folds
knn.model.cv <- train.cv(model.formula, 'knn', 5)

# print the model
knn.model.cv
```

Tune KNN regressor

```{r}
model.formula <- MonthlyIncome ~ TotalWorkingYears:JobLevel + JobLevel + JobLevel:Age + TotalWorkingYears:JobRole + JobRole

#model.formula <- MonthlyIncome ~ TotalWorkingYears:JobLevel + JobLevel + TotalWorkingYears:JobRole
#c(2,3,5,7,9,11,13,15)
knn.tuningGrid <- expand.grid(k = seq(1:15))

# Set up repeated k-fold cross-validation
train.control <-trainControl(method = "cv", number = 5)
# Train the model
model.cv <-dfTrain %>% train(model.formula,
                 data = .,
                 method ='knn',
                 trControl = train.control,
                 tuneGrid = knn.tuningGrid)
# print model summary
model.cv
```

Plot k VS RMSE to visualize model tuning

```{r}
k.values <- model.cv$results$k
RMSE <- model.cv$results$RMSE
Rsquared <- model.cv$results$Rsquared

knn.tune <- data.frame(k.values, RMSE, Rsquared)
p1 <- knn.tune %>% 
  ggplot(aes(x = k.values, y = RMSE)) + geom_point() + 
  scale_fill_few(palette = 'Dark') + 
  ggtitle('RMSE vs k for KNN Tuning') +
  xlab('k Parameter')

p2 <- knn.tune %>% 
  ggplot(aes(x = k.values, y = Rsquared)) + geom_point() + 
  scale_fill_few(palette = 'Dark') + 
  ggtitle('R Squared vs k for KNN Tuning') +
  xlab('k Parameter')

grid.arrange(p1,p2, ncol = 2)
```



