---
title: "Modeling Income"
author: "Stuart Miller"
date: "August 9, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}


# import libraries
library(knitr)
library(tidyverse)
library(naniar)
library(Hmisc)
library(GGally)
library(gridExtra)
library(RColorBrewer)
library(gplots)
library(corrplot)
library(ggthemes)
library(caret)

set.seed(3456)

# import helper functions
source('../helper/data_munging.R')
source('../helper/visual.R')

# read in data
train <- read_csv('../data/CaseStudy2-data_train.csv')
```

## Data Partitioning

The training dataset will be split into a training set and a test set. The training set `dfTrain` will be used for model cross validation. The test set will be used for final model selection.

```{r}
# split off a test set
trainIndex <- createDataPartition(train$MonthlyIncome , p = .75, 
                                  list = FALSE, 
                                  times = 1)
dfTrain <- train[trainIndex,]
dfTest <-  train[-trainIndex,]
```

## Model Construction

From EDA, it appears that monthly income is correlated to `TotalworkingYears`, `Age`, `YearsAtCompany`, `YearsInCurrentRole`, and `YearsWithCurrentManager`.

From the factors:

* `JobLevel` appears to partion `TotalWorkingYears` and `MonthlyIncome` very well.


```{r}
#model.linear <- dfTrain %>% lm(MonthlyIncome ~ TotalWorkingYears*JobLevel + JobLevel, data = .)

model.linear <- dfTrain %>% lm(MonthlyIncome ~ TotalWorkingYears:JobLevel + JobLevel + JobRole, data = .)

summary(model.linear)

dfTrain  %>% basic.fit.plots(., model.linear)
```


```{r, cv_pipe}

model.formula <- MonthlyIncome ~ TotalWorkingYears:JobLevel + JobLevel + TotalWorkingYears:JobRole

# Set up repeated k-fold cross-validation
train.control <-trainControl(method = "cv", number = 5)
# Train the model
model.cv <-dfTrain %>% train(model.formula,
                 data = .,
                 method ='lm',
                 trControl = train.control)
# print model summary
model.cv
```

```{r}
model.formula <- MonthlyIncome ~ TotalWorkingYears:JobLevel + JobLevel + TotalWorkingYears:JobRole

# Set up repeated k-fold cross-validation
train.control <-trainControl(method = "cv", number = 5)
# Train the model
model.cv <-dfTrain %>% train(model.formula,
                 data = .,
                 method ='knn',
                 trControl = train.control)
# print model summary
model.cv
```
```


